ms_figures

### 2018-05-07 man/ms_figures.Rmd
updates figures

**Figure 1**. Distribution of *Quercus pyrenaica* forests in Iberian Peninsula (a) and in Sierra Nevada mountain (b). Different colours indicate oak population cluster's identified in Sierra Nevada [@PerezLuque2015]. For each population, a grid with the MODIS pixels is shown (see material and methods). Detailed location of the dendroecological sampling sites: northern (San Juan, SJ) (c) and southern ones (Cáñar: CA-Low and CA-High) (d). Colour Orthophotography of 2009 from Regional Ministry of the Environment, Regional Government of Andalusia.

@@

##### 
```{r, echo=FALSE}
cro_sites <- read.csv(here("data/cronos_medias", "cronos_sites.csv"), header = TRUE, sep = ',')

m1 <- lm(bai_mean ~ year, df)
summary(m1)
r2 <- format(summary(m1)$r.squared, digits = 3)
```

**Figure 4.** Basal Area Increment (BAI) chronologies of *Q. pyrenaica* for northern population (SJ; *green*) and southern ones: low-elevation (CA-Low; *pink*) and high-elevation (CA-High, *purple*) sites. Shading areas coorespond to standard error of the mean. Number of series are displayed in the upper plot. We only show chronologies with # trees > 5. Linear trend since 1975 is shown for southern high-elevation site (CA-High) ($r_2$ = `r2`).

```{r, warning=FALSE, out.extra='angle=90'}
cro_sites <- read.csv(here("data/cronos_medias", "cronos_sites.csv"), header = TRUE, sep = ',')

@@

@@

##### 
**Figure 5.** Residual Tree-ring chronologies obtained for the *Q. pyrenaica* sites. Dashed red lines indicate the start of the reliable period (EPS > 0.85). Dotted black lines showing the three of most recent severe drought years (1995, 2005 and 2012).

@@

##### 
**Figure 6.** Correlation coefficients obtained by relating tree-ring residual chronologies (RWI) of *Q. pyrenaica* and monthly climatic data: precipitation (a), SPEI (b), maximun (c) and minimun (d) temperatures. *green* bars: northern site (SJ); *light blue* bars: low-elevation southern site; and *dark blue* bars: high-elevation shouthern site. Asteriks indicate significant ($P < 0.05$) correlation coefficients.

@@

clima_ring <- ddf %>% ggplot(aes(x=id, y=coef, group = site)) + 
  geom_hline(yintercept = 0, colour="gray") +
  geom_bar(aes(fill=site), stat="identity", position = "dodge") +
  facet_wrap(~v_name, labeller = as_labeller(label_var)) + 
  geom_text(aes(label = sig, x = id, y = ifelse(coef > 0, (coef + 0.02), (coef - 0.05))), 
            position = position_dodge(.9), size = 6) + 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = 0.3),
        legend.position = "bottom",
        strip.background = element_rect(fill=NA, colour=NA),
        strip.text.x = element_text(size = 10, face = "bold")) + 
  scale_x_continuous(breaks = unique(ddf$id), labels = unique(ddf$month_name)) +
  scale_y_continuous(limits = c(-0.4, 0.8), 
                     breaks = c(-0.4, -0.2, 0, 0.2, 0.4, 0.6,0.8)) + 
  scale_fill_manual(values = c("#B2DF8A","#1F78B4","#A6CEE3")) + 
  ylab('Correlation')

@@

##### 
**Appendix S3.** Drought events for Sierra Nevada based on SPEI index. A drought event starts in the month when SPEI falls below the threshold of -1.28 [@Pascoa2017]. A drought event is considered only when SPEI value are below threshold for at least two consecutive months [*e.g* @Spinoni2015; Spinoni2017a; @Pascoa2017]. The ***duration*** of a drought event is the number of consecutive months with the SPEI lower than a certain threshold. ***Severity*** of a drought event is the sum of the SPEI values (absolute values) during the duration of the drought event. ***Intensity*** and ***Lowest SPEI** refer to the mean and lowest value of SPEI respectively during the drought event duration.

>>>>

**Figure 1**. Distribution of *Quercus pyrenaica* forests in Iberian Peninsula (a) and in Sierra Nevada mountain (b). Different colours indicate oak population cluster's identified in Sierra Nevada [@PerezLuque2015]. For each population, a grid with the MODIS pixels is shown (see material and methods). Detailed location of the dendroecological sampling sites: northern (San Juan, SJ) (c), and southern ones (Cáñar: CA-Low and CA-High) (d). Colour orthophotography of 2009 from Regional Ministry of the Environment, Regional Government of Andalusia.

@@

##### 
```{r, warning=FALSE}
cro_sites <- read.csv(here("data/cronos_medias", "cronos_sites.csv"), header = TRUE, sep = ',')

@@

m1 <- lm(bai_mean ~ year, df)
# summary(m1)
myr2 <- format(summary(m1)$r.squared, digits = 3)

**Figure 4.** Basal Area Increment (BAI) chronologies of *Q. pyrenaica* for northern population (SJ; *green*) and southern ones: low-elevation (CA-Low; *pink*) and high-elevation (CA-High, *purple*) sites. Shading areas coorespond to standard error of the mean. Number of series are displayed in the upper plot. We only show chronologies with # trees > 5. Linear trend since 1975 is shown for southern high-elevation site (CA-High) ($r_2$ = `r myr2`).

```{r, warning=FALSE, out.extra='angle=90'}

@@

##### 
**Figure 5.** Residual tree-ring chronologies obtained for the *Q. pyrenaica* sites. Dashed red lines indicate the start of the reliable period (EPS > 0.85). Dotted black lines showing the three of most recent severe drought years (1995, 2005 and 2012).

@@

##### 
**Figure 6.** Correlation coefficients obtained by relating tree-ring residual chronologies (RWI) of *Q. pyrenaica* and monthly climatic data: precipitation (a), SPEI (b), maximun (c) and minimun (d) temperatures. *green* bars: northern site (SJ); *light blue* bars: low-elevation southern site (CA-Low); and *dark blue* bars: high-elevation shouthern site (CA-High). Asteriks indicate significant ($P < 0.05$) correlation coefficients.

@@

label_site <- c("SJ" = "SJ",
                "caH" = "CA-High",
                "caL" = "CA-Low")

clima_ring <- ddf %>% ggplot(aes(x=id, y=coef, group = site)) + 
  geom_hline(yintercept = 0, colour="gray") +
  geom_bar(aes(fill=site), stat="identity", position = "dodge") +
  facet_wrap(~v_name, labeller = as_labeller(label_var)) + 
  geom_text(aes(label = sig, x = id, y = ifelse(coef > 0, (coef + 0.02), (coef - 0.05))), 
            position = position_dodge(.9), size = 6) + 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = 0.3),
        legend.position = "bottom",
        strip.background = element_rect(fill=NA, colour=NA),
        strip.text.x = element_text(size = 10, face = "bold")) + 
  scale_x_continuous(breaks = unique(ddf$id), labels = unique(ddf$month_name)) +
  scale_y_continuous(limits = c(-0.4, 0.8), 
                     breaks = c(-0.4, -0.2, 0, 0.2, 0.4, 0.6,0.8)) + 
  scale_fill_manual(values = c("#B2DF8A","#1F78B4","#A6CEE3"), labels = label_site) + 
  ylab('Correlation')

@@

##### 
**Appendix S3.** Drought events for Sierra Nevada based on SPEI index. A drought event starts in the month when SPEI falls below the threshold of -1.28 [@Pascoa2017]. A drought event is considered only when SPEI value are below threshold for at least two consecutive months [*e.g.* @Spinoni2015; @Spinoni2017a; @Pascoa2017]. The ***duration*** of a drought event is the number of consecutive months with the SPEI lower than a certain threshold. ***Severity*** of a drought event is the sum of the SPEI values (absolute values) during the duration of the drought event. ***Intensity*** and ***Lowest SPEI*** refer to the mean and lowest value of SPEI respectively during the drought event duration.
